### 2020-08-18 manuscript/manuscript.rmd
move some cat computation to kernel, re-run kernel

---
bibliography: manuscript.bib
csl: nature.csl
output:
  html_document: default
  pdf_document: default
  word_document: default
  github_document: default
---

@@

```{r n_cat}
# Return the allocation midpoint, ie the percent of sites that are allocated to the
# 50% of the least frequent categories
allocation_midpoint = function ( pb_summary ) {
  x = pb_summary %>% pull( count ) %>% sort(decreasing = FALSE)
  x = x/ sum(x)
  y = cumsum( x )
  return ( round( median( y ) *100, 2 ) )
}

# Parse the last sample from chain 1 of each analysis
phil_cat_c1 =
  parse_phylobayes_last_sample("../trees_new/frequency/subsampled_Philippe2009_only_choanozoa.phy_Poisson_CAT_Chain_1.chain")

phil_cat60_c1 =
  parse_phylobayes_last_sample("../trees_new/frequency/subsampled_Philippe2009_only_choanozoa.phy_Poisson_nCAT60_Chain_1.chain")

whel_cat_c1 =
  parse_phylobayes_last_sample("../trees_new/frequency/subsampled_Whelan2017_strict.phy_Poisson_CAT_Chain1.chain")

whel_cat60_c1 =
  parse_phylobayes_last_sample("../trees_new/frequency/subsampled_Whelan2017_strict.phy_Poisson_CAT60_Chain_1.chain")

# Create a single tibble with summaries of all analyses
pb_summaries = list(
  summarise_sample( phil_cat_c1 ) %>%
    mutate ( chain=1, matrix="Philippe2009", model="Poisson+CAT"),
  summarise_sample( phil_cat60_c1 ) %>%
    mutate ( chain=1, matrix="Philippe2009", model="Poisson+nCAT60"),
  summarise_sample( whel_cat_c1 ) %>%
    mutate ( chain=1, matrix="Whelan2017_strict", model="Poisson+CAT"),
  summarise_sample( whel_cat60_c1 ) %>%
    mutate ( chain=1, matrix="Whelan2017_strict", model="Poisson+nCAT60")
) %>%
  bind_rows() %>%
  mutate( analysis = paste(matrix, model, sep=" ")) %>%
  mutate( model=factor(model, levels=c("Poisson+nCAT60", "Poisson+CAT")) )

pb_frequencies = pb_summaries %>% select( starts_with("aa.") ) %>% data.matrix()

# Identify the midpoint of each set of allocations
mid_phil_cat =
  pb_summaries %>%
  filter( matrix=="Philippe2009" ) %>%
  filter( model=="Poisson+CAT" ) %>%
  allocation_midpoint()

mid_phil_ncat60 =
  pb_summaries %>%
  filter( matrix=="Philippe2009" ) %>%
  filter( model=="Poisson+nCAT60" ) %>%
  allocation_midpoint()

mid_whel_cat =
  pb_summaries %>%
  filter( matrix=="Whelan2017_strict" ) %>%
  filter( model=="Poisson+CAT" ) %>%
  allocation_midpoint()

mid_whel_ncat60 =
  pb_summaries %>%
  filter( matrix=="Whelan2017_strict" ) %>%
  filter( model=="Poisson+nCAT60" ) %>%
  allocation_midpoint()

n_categories_phil_cat =
  pb_summaries %>%
  filter( matrix=="Philippe2009" ) %>%
  filter( model=="Poisson+CAT" ) %>%
  nrow()

n_categories_whel_cat =
  pb_summaries %>%
  filter( matrix=="Whelan2017_strict" ) %>%
  filter( model=="Poisson+CAT" ) %>%
  nrow()

# Perform global MDS analysys
fit = cmdscale( dist( pb_frequencies ) ,eig=TRUE, k=2)
pb_summaries %<>% mutate( x_global = fit$points[,1], y_global = fit$points[,2] )

>>>>

---
bibliography: manuscript.bib
csl: nature.csl
output:
  word_document: default
  pdf_document: 
    latex_engine: xelatex
  html_document: default
  github_document: default
---

@@

```{r n_cat}
